Uncovering underlying musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-03-29 introduction/Subsections/Motivation.tex
Updates from Overleaf

As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them using DN.  I am eager to learn how DNNs listen to music. I am deeply interested in learning how to retrieve embedded information within music.

\section{About aural skills and high-level perceptual}

@@

I have consistently been inspired by researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker\cite{}, or by challenging it, as exemplified by George Russell\cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.

Schenkerian Analysis:
Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, analyzes tonal music focusing on its underlying structure. It seeks to reveal the hierarchical relationships between pitches, based on the premise that all tonal music has a fundamental structure known as the "Ursatz" or "basic shape." The Ursatz consists of a stepwise descending line (Urlinie) supported by a bass arpeggiation (Bassbrechung). Schenkerian Analysis reduces a musical composition to its essential elements, enabling the analyst to observe how the work's various layers contribute to the overall structure. It is worth mentioning that such analysis is done in the symbolic domain.

@@

>>>>

\section{About music aural skills and high-level perception}

I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker \cite{}, or by challenging it, as exemplified by George Russell \cite{LydianRussell}. Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation. Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.

@@

Schenkerian Analysis, devised by Austrian music theorist Heinrich Schenker, explores tonal music's underlying structure by concentrating on the hierarchical relationships between pitches. Based on the idea that all tonal music shares a fundamental structure called "Ursatz" or "basic shape," the method identifies the stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung). Schenkerian Analysis simplifies a musical piece to its core elements, allowing analysts to examine how different layers contribute to the overall structure. Key concepts include prolongational levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure). Although criticized for reducing all tonal works to a few background structures, Schenker emphasizes the importance of individual elaboration in determining a work's identity and meaning.

Anstieg (Initial Ascent): Ascending motion leading to the primary tone of the fundamental line.
Arpeggiation (Brechung): Elementary elaboration of a harmony.
Background (Hintergrund): The structural level of the fundamental structure.
Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forming the harmonic content of the background of tonal musical pieces.
Chord of Nature (Klang): The complex sound consisting of the first five notes of the harmonic series, suggesting a model for the major triad.
Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
Foreground (Vordergrund): The surface level of musical structure in Schenkerian analysis.
Fundamental Line (Urlinie): The melodic aspect of the fundamental structure, a stepwise descent from one of the triad notes to the tonic.
Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad is able to govern spans of music when not physically sounding.
Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middleground, and foreground.
Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space that is filled with passing and neighbor notes.
Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
Voice Leading: The study of the principles that govern the progression of the component voices of a composition both separately and in combination.
The glossary also includes related articles, references, and external links for further reading and understanding of Schenkerian analysis.

@@

\subsection{Assumptions}
